Title here

### 2016-12-11 portfolio/text/ms.Rmd
Edit intro/results

Using a unique dataset collected over 30 years (1985--2014) on individuals,
rather than fleets or vessels, we examine how revenue and revenue variability of
individuals is affected by diversification. By tracking individuals rather than
vessels we can track people that switch fishery permits over time or use
multiple vessels. Similarly, we are able to disentangle fishers that share the
same vessel. We develop and apply a hierarchical Bayesian model to understand
the effect of diversity on both individual revenue and revenue variability that
builds on results from vessel [@kasperski2013], fleet [@sethi2012b], and
community-level [@sethi2014] variability. Our model controls for fishing effort
and latent time effects (e.g. changing environmental conditions), simultaneously
estimates the effect of species diversity on individual revenue and revenue
variability, and estimates effects both within and across fishing strategies
(sets of similar licenses or permits). To our knowledge, this is the first
application of this type of model in any natural resource field.

Our hierarchical variance-function regression model [@davidian1987; @hall1989]
simultaneously models changes in the mean and variance of individual revenue as
a function of covariates. Whereas traditional hierarchical linear models assume
homoscedasticity --- that the residual variance does not vary systematically ---
the variance-function regression model allows the variance to be heteroscedastic
and vary as a function of predictors. Our specific model allows the revenue rate
of return (log of the ratio of year-to-year revenue) and the revenue variability
(the standard deviation of this revenue rate of return) to vary by fishing
strategy (fishing permit sets), fishing effort (season length), and levels of
species diversification.

@@

We first evaluated trends in revenue and diversification over time for
individuals fishing commercially in Alaska from 1985--2014 (Fig. \ref{fig:ts}A).
The majority (70--90%) of fishers hold single permits, with a slight increase in
single-permit holders since 2000 (Fig. \ref{fig:ts}C). This overall trend is
most sensitive to halibut or salmon permit holders --- compared to other
fisheries, halibut permit holders are more likely to hold halibut plus other
permits, whereas salmon permit holders are more likely to hold only one permit
(Fig. \ref{fig:ts}C). Despite making up only 10--30% of the individuals,
multiple permit holders make approximately half of the overall revenue (Fig.
\ref{fig:ts}B). The mean effective fished species diversity of this revenue
declined somewhat from 1980--2000 but has since remained steady (Fig.
\ref{fig:ts}D). However, this trend appears to be driven by an increase in
salmon specialists in the 1980s and 1990s --- the trend disappears if salmon
license holders are excluded (Fig. \ref{fig:ts}D).

Revenue variability decreases exponentially with higher mean fished species
diversity across permit sets (Fig. \ref{fig:across}). Controlling for effort,
strategies with one unit higher mean effective species diversity had on average
`r h1[[2]]`% (`r h1[[1]]`--`r h1[[3]]`% 95% CI) lower variability. This pattern
looks qualitatively similar with or without individuals targeting salmon. As
examples, variability was highest for the herring roe gillnet and king crab
fisheries. Most of the strategies with the lowest estimated revenue variability
combined halibut with a salmon permit and had high levels of fished species
diversity (Fig. \ref{fig:across}).

@@

The management of the Alaskan halibut and sablefish fisheries was converted to
individual fishery quotas (IFQ) in 1994. This catch share system... TODO. We
refit our models allowing all permit-level effects to vary separately before and
after the introduction of IFQs for strategies involving halibut and sablefish
permits. The introduction of IFQs reduced variability by ~25% (XX--XX 95% CI)
for individuals with only halibut or sablefish permits (Fig. S\ref{fig:ifq}A).
Furthermore, for most strategies, the effect of increased revenue variability
associated with changing species diversity became stronger after the
introduction of IFQs (Fig. S\ref{fig:ifq}B). This was especially true for
individuals fishing only halibut or sablefish and less so for individuals
combining halibut or sable fish with a salmon permit (Fig. S\ref{fig:ifq}B).

>>>>

Using a unique dataset collected over 30 years (1985--2014) on individuals,
rather than fleets or vessels, we examine how revenue and revenue variability of
individuals is affected by diversification. By tracking individuals we can track
people that switch fishery permits over time or use multiple vessels. Similarly,
we can disentangle fishers that share the same vessel. We develop and apply
a hierarchical Bayesian model to understand the effect of fished species
diversity on individual revenue and revenue variability that builds on results
from vessel [@kasperski2013], fleet [@sethi2012b], and community-level
[@sethi2014] variability.

Our model is a variance-function regression model [@davidian1987; @hall1989],
which simultaneously models changes in the mean and variance of individual
revenue as a function of covariates. Whereas traditional hierarchical linear
models assume homoscedasticity --- that the residual variance does not vary
systematically --- the variance-function regression model allows the variance to
be heteroscedastic and vary as a function of predictors. Our specific model
simultaneously estimates the effect of species diversity on individual revenue
and revenue variability, and estimates effects both within and across fishing
strategies (sets of similar licenses or permits). At the same time, it controls
for fishing effort and latent time effects (e.g. changing environmental
conditions). To our knowledge, this is the first application of this type of
model in any natural resource field.

@@

We evaluated trends in revenue and diversification over time for individuals
fishing commercially in Alaska from 1985--2014 (Fig. \ref{fig:ts}A). The
majority (70--90%) of fishers hold single permits, with a slight increase in
single-permit holders since 2000 (Fig. \ref{fig:ts}C). This overall trend is
most sensitive to halibut or salmon permit holders --- compared to other
fisheries, halibut permit holders are more likely to hold halibut plus other
permits, whereas salmon permit holders are more likely to hold only one permit
(Fig. \ref{fig:ts}C). Despite making up only 10--30% of the individuals,
multiple permit holders earn approximately half the overall revenue (Fig.
\ref{fig:ts}B). The mean effective fished species diversity of this revenue
declined somewhat from 1980--2000 but has since remained steady (Fig.
\ref{fig:ts}D). However, this trend appears to be driven by an increase in
salmon specialists in the 1980s and 1990s --- the trend disappears if salmon
license holders are excluded (Fig. \ref{fig:ts}D).

Individual revenue variability decreases exponentially with higher mean fished
species diversity across permit sets (Fig. \ref{fig:across}). Controlling for
effort, strategies with one unit higher mean effective species diversity had on
average `r h1[[2]]`% (`r h1[[1]]`--`r h1[[3]]`% 95% CI) lower variability. This
pattern looks qualitatively similar with or without individuals targeting
salmon. As examples, variability was highest for the herring roe gillnet and
king crab fisheries. Most of the strategies with the lowest estimated revenue
variability combined halibut with a salmon permit and had high levels of fished
species diversity (Fig. \ref{fig:across}).

@@

Alaskan halibut and sablefish fisheries were converted to individual fishery
quota (IFQ) management in 1994. This catch share system... TODO. We refit our
models allowing all permit-level effects to vary separately before and after the
introduction of IFQs for strategies involving halibut and sablefish permits. The
introduction of IFQs reduced variability by ~25% (XX--XX 95% CI) for individuals
with only halibut or sablefish permits (Fig. S\ref{fig:ifq}A). Furthermore, for
most strategies, the association changing species diversity with increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\ref{fig:ifq}B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\ref{fig:ifq}B).
